One more attempt on ArXe

### 2015-10-30 experimental.tex
Text überarbeitet

\section{Experimental}
%
\begin{table}
\caption{
Expansion parameters used for cluster production. Here, Xe$_{in}$ is the fraction (particle number) of Xe in the expanding gas before the expansion, $T$ the nozzle temperature, and $p$ the stagnation pressure. Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to hypothetical cluster sizes yielded with an expansion of the respective pure gas at the conditions given. These values are calculated as in ref.\ \protect\citenum{hagena1981}. Due to the much lower freezing point of Ar, we basically have an Ar seeded expansion of Xe gas. We therefore expect actual cluster sizes in-between the two limiting values given. Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model used.
}
\label{tab:cluster}

\begin{tabular}{l c c c r r}
%
\toprule
  label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
%
\midrule
% Ar, from Marko 
Ar (1)  & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar (2)  & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
 (a) & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
 (b) & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
 (c) & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
 (d) & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
 (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset ber?cksichtigt
Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\midrule
% 1103 653
1103, only coinc  & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
  & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
  & 5.0 &  167   & 0.68  &  26  &  451 \\
\midrule
% 1004 867
1004, 867  & 2.5 &  154   & 2.12  &  920 & 15760\\
% 1004 868
868  & 2.5 &  158   & 1.50  &  355 &  6090\\
% 1004 886
886  & 2.5 &  161   & 2.41  &  980 & 16770\\
% 1004 858
858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
%
\bottomrule
\end{tabular}
\end{table}
%
%
The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion} A detailed description can be found in Ref. \citenum{arion}, and here we focus on those details specific for the current experiment. Commercial Ar and Xe gas was used. Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. Expansion parameters and mean cluster sizes according to an empirical model are given in Tab.\ \ref{tab:cluster}. We note that currently no such  model for heterogeneous expansions exists. We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.

The expansion chamber for the supersonic is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Tab.\ \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Tab.\ \ref{tab:cluster}). Linearly, horizontally polarized radiation was used.

>>>>

\section{Experimental}
%
\begin{table}
\caption{
Expansion parameters used for cluster production. Here, Xe$_{in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to cluster sizes arrived at by an expansion of the respective pure gases at the given conditions. These values are calculated as in ref.\ \protect\citenum{hagena1981}. Due to the much lower freezing point of Ar, we basically have an Ar seeded expansion of Xe gas. We therefore expect actual cluster sizes in-between the two limiting values given. Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model used.
}
\label{tab:cluster}

\begin{tabular}{l c c c c r r}
%
\toprule
  & size label  &  Xe$_{in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
%
\midrule
% Ar, from Marko 
Ar &  & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar &  & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
ArXe & S & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
ArXe & M & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
ArXe & L & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
ArXe & S & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
ArXe & M & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset ber?cksichtigt
Xe &  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\midrule
% 1103 653
ArXe & M & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
ArXe & L & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
ArXe & S  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
ArXe & L  & 5.0 &  167   & 0.68  &  26  &  451 \\
\midrule
% 1004 867
1004, 867 &  & 2.5 &  154   & 2.12  &  920 & 15760\\
% 1004 868
868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
% 1004 886
886 & XL & 2.5 &  161   & 2.41  &  980 & 16770\\
% 1004 858
858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
%
\bottomrule
\end{tabular}
\end{table}
%
%
The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion} 
% Leave this citation in place to avoid Latex error
A detailed description can be found in Ref. \citenum{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
Expansion parameters and mean cluster sizes, according to an empirical model, are given in Tab.\ \ref{tab:cluster}. 
We note that currently no empirical model for cluster sizes in a heterogeneous gas expansion exists. 
We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.

The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). 
At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} 
Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Tab.\ \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Tab.\ \ref{tab:cluster}). 
Linearly, horizontally polarized radiation was used. 
The storage ring was operated in single bunch conditions.

### 2015-10-30 structures.tex
Text überarbeitet

From the experimental results we can obtain two hints for the cluster
structure: the minimum size and the xenon content. We will in the following
use these to construct possible cluster structures for which we will later
simulate the ICD and ETMD spectra. At this step we put in whatever structure
we might think of and hope to be able to exclude some of them by comparison of
the ICD and ETMD spectra to the experimental electron-electron coincidence
spectra.

The expected mean argon cluster sizes
were estimated and collected in Table \ref{table:cluster}.
In case of the smaller clusters measured
these expectation values range from \unit[3 -- 21]{Ar atoms} for
expansion of pure argon. The cluster sizes of a mixed gas are unknown but
for xenon as the second component the cluster sizes can be expected to
be larger than those of pure argon due to the higher polarizability
and hence larger cohesive energy of xenon. All clusters
contributing to the coincidence spectrum
do contain at least one xenon atom, otherwise there would be no signal at all.
In an expansion a large variance of clusters and with different structures
is produced. However, for small clusters consisting of less than
approximately \unit[1000]{atoms} so-called \emph{islands of stability} were
found for clusters with icosahedral shape. This means, that the probability
to find and measure such a cluster is higher than a different structure.
We therefore started from icosahedral structures and substituted atoms
in the clusters by
argon / xenon atoms or added these to a given structure close to the wanted
position. Afterwards the cluster structures were optimized using the
UFF force field \cite{} implemented in
Avogadro \cite{} for a structure optimization.

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_2_overview.pdf}
 \caption{Cluster structures with 13 argon atoms and two additional xenon
          atoms on different surfaces of the argon icosahedron:
          \textbf{a)} closest possible \textbf{b)} middle \textbf{c)}
          furthest away.}
 \label{figure:cluster_2_overview}
\end{figure}

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_3_overview.pdf}
 \caption{Cluster structures based on 55 atoms icosahedral cluster structure.
          \textbf{a)} 1 xenon atom on the surface of a 55 atoms icosahedral
          argon cluster. \textbf{b)} six xenon atoms inside a 55 atoms cluster
          grouped on one side. \textbf{c)} six xenon atoms distributed
          in a 55 atoms cluster. }
 \label{figure:cluster_3_overview}
\end{figure}

As discussed in the introduction, the small clusters are very likely
to deviate from a core-shell structure with a xenon core surrounded
by argon shells as observed for large clusters. We therefore start from
argon clusters of 13 or 55 atoms and modify them in one of the following
ways:

\begin{itemize}
 \item add one xenon atom on top of a surface / edge / vertex of
       the argon core as for example shown in
       Figure \ref{figure:cluster_3_overview} Panel a)
       for one additional xenon atom
       on top of surface of a \unit[55]{atoms} argon core
 \item substitute one argon atom in a surface / edge / vertex position if
       possible
 \item substitute one or two argon atoms in the core of the argon cluster
       by xenon atom(s) for the simulation of the core-shell structure
 \item add two xenon atoms on top of surfaces of a 13 atoms argon core
       in different relative positions (see Figure
       \ref{figure:cluster_2_overview})
       in order to achieve a xenon content in the cluster close to the
       measured one shown in Table \ref{table:cluster}
 \item substitute six argon atoms of a 55 atoms argon cluster by xenon
       atoms either grouping them or scattering them througout the cluster
       (see Figure \ref{figure:cluster_3_overview} Panels b) and c)) in order to
       achieve a xenon content in the cluster close to the experimental one
\end{itemize}

Furthermore we constructed a core-shell structure with a core of
1415 xenon atoms and one additional complete layer of argon atoms for
comparison with the largest measured ArXe clusters.

>>>>

From the experimental results we can obtain two hints for the cluster
structure: the minimum size and the xenon content. In the following we will 
use these to construct possible cluster structures for which we will later
simulate the ICD and ETMD spectra. At this point we put in a variety of structures,
in the hope to exclude some of them by comparison of
the ICD and ETMD spectra to the experimental ones.

In our previous study\cite{Fasshauer13} the ArXe clusters were assumed
to be large, having more than 1500 atoms. The model structures assumed
an fcc structure and not an icosahedral structure, which is energetically
favoured for small clusters.
Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size, start our search for model structures from there.
%
%Additionally,
%the expectation value for the number of xenon atoms relies on a pure
%xenon gas. Since the xenon content in the mixed gas is much lower, also
%the number of xenon atoms can be expected to be by far less. We therefore
%start from the estimated number of atoms in the cluster after expansion
%of pure argon gas.
%We therefore rethink the possible cluster structures.
%Furthermore, the theoretical prediction did not match the experimental results.
%Since the spectra are strongly depending on the cluster structure as shown in
%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
%we rethink the possible cluster structures.
%
For the smaller clusters measured,
these expectation values range from \unit[3--21]{Ar atoms}. 
The cluster sizes for expansion of a mixed gas are unknown, but
for xenon as the second component a larger size is expected compared to a
pure argon expansion, due to the higher polarizability
and hence larger cohesive energy of xenon. All clusters
contributing to the coincidence spectrum
contain at least one xenon atom, as otherwise decay by ICD or ETMD is energetically not allowed.

In a gas expansion a range of clusters sizes with different structures is produced. 
However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had a (slightly) enhanced abundance over other sizes. 
We therefore started from icosahedral structures and produced mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms to a given structure close to the desired position. 
After that, the cluster structures were optimized using the UFF force field method \cite{} implemented in the 
Avogadro programme \cite{}.
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_2_overview.pdf}
 \caption{Cluster structures composed of 13 argon atoms and two additional xenon
          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
          (a) closest possible, (b) middle, (c) furthest away.}
 \label{figure:cluster_2_overview}
\end{figure}
%
\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_3_overview.pdf}
 \caption{Cluster structures derived from a 55 atom icosahedral structure:
          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
          grouped on one side, (c) six xenon atoms distributed randomly
          in a 55 atoms cluster.}
 \label{figure:cluster_3_overview}
\end{figure}

As discussed in the introduction, the small clusters will likely
deviate from a core-shell structure with a xenon core surrounded
by argon shells, as observed for large clusters.\cite{tchaplyguinearxe,Vach_1999} We therefore start from
argon clusters of 13 or 55 atoms, and modify them in one of the following
ways:
%
\begin{itemize}
 \item add one xenon atom on top of a surface / edge / vertex of
       the argon core, as for example shown in
       Figure \ref{figure:cluster_3_overview} a)
       for one additional xenon atom
       on top of surface of a \unit[55]{atoms} argon core,
 \item substitute one argon atom in a surface / edge / vertex position,
 \item substitute one or two argon atoms in the core of the argon cluster
       by xenon atom(s) for the simulation of the core-shell structures,
 \item add two xenon atoms on top of surfaces of a 13 atoms argon core
       in different relative positions (see Figure
       \ref{figure:cluster_2_overview}),
       in order to achieve a xenon content in the cluster close to the
       measured one (see below),
 \item substitute six argon atoms of a 55 atoms argon cluster by xenon
       atoms either grouping them or distributing them througout the cluster
       (see Figure \ref{figure:cluster_3_overview} b) and c)) in order to
       achieve a xenon content in the cluster close to the measured one.
\end{itemize}
%
Furthermore, for comparison with the largest measured ArXe clusters, we constructed a core-shell structure with a core of 1415 xenon atoms and one additional complete layer of argon atoms.
